---
title: "R Markdown and Leaflet"
author: "Peng"
date: "December 25, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Introduction
Leaflet is one of the most popular Javascript libraries for creating interactive maps. The leaflet R package allows you to create your own leaflet maps without needing to know any Javascript. You need to install the leaflet package in R using `install.packages("leaflet")`.

This report features an interactive map that displaying the top 5 wildfires in southern California and their causes.

```{r, eval=FALSE}
library(leaflet)

m_fires %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(lat=34.407365, lng=-119.081787 , 
                        popup="Thomas", color = "green")%>%
  addCircleMarkers(lat=33.016667, lng=-116.683333 , 
                        popup="Cedar",  color = "red")%>%
  addCircleMarkers(lat=34.7159, lng=-119.7828 , 
                        popup="Zaca", color = "red")%>%
  addCircleMarkers(lat=34.498635, lng=-119.347444 , 
                        popup="Matilija", color = "blue")%>%
  addCircleMarkers(lat=33.0797, lng=-116.6861 , 
                        popup="Witch", color = "red")%>%
  addLegend(labels = c("Natrual","Human","Under Investigation"), colors = c("blue", "red", "green"))
```