---
title: "R Markdown Presentation & Plotly"
author: "Peng"
date: "December 31, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Datasets: mtcars

Motor Trend Car Road Tests(mtcars): The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).


No.| Variable | Description
---|----------|----------------------
1. |mpg      | Miles/(US) gallon
2. |cyl	     | Number of cylinders
3. |hp	     | Gross horsepower
5. |wt	     | Weight (1000 lbs)
6. |am	     | Transmission (0 = automatic, 1 = manual)

## Datset Summary

```{r cars, echo = TRUE}
summary(mtcars[,c('mpg', 'cyl', 'hp', 'wt')])
```

## Boxplot

```{r, warning=FALSE, message=FALSE}
library(plotly)

mtcars$am[mtcars$am==0] <- 'Auto'
mtcars$am[mtcars$am==1] <- 'Manual'

plot_ly(mtcars, y = ~mpg, type = "box", color = ~factor(am))
```

## Scatter Plot

```{r, warning=FALSE, message=FALSE}
library(plotly)

mtcars$am[mtcars$am==0] <- 'Auto'
mtcars$am[mtcars$am==1] <- 'Manual'

plot_ly(
    mtcars, x = ~wt, y = ~mpg, type = "scatter", 
    color = ~factor(am), size = ~hp
)
```



## Thank you!